%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/tramhuuducvn}{\Large Tram Huu Duc}} & Email: \href{mailto:tramhuuduc.vn@gmail.com}{tramhuuduc.vn@gmail.com}\\
  \href{https://github.com/tramhuuducvn}{https://github.com/tramhuuducvn} & Mobile: \href{tel:+84375157298}{0375157298} \\
\end{tabular*}

%-----------SUMMARY-----------------
\section*{Summary}
Software engineer with 2+ years of experience in building backend services using Spring Boot and developing mobile applications with React Native. Interested in clean code, API design, and learning from collaboration and testing practices.


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Science}{Ho Chi Minh City}
      {Software Engineering; GPA: 3.2}{September 2019 -- July 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {KMS Technogy}{Ho Chi Minh City}
      {Software Engineer}{September 2023 -- Present}
      \resumeItemListStart
        \resumeItem{RESTful API Development}
          {Designed and implemented RESTful APIs for internal services and third-party integrations, ensuring compliance with insurance domain standards.}
        \resumeItem{Spring AOP Logging}
          {Implemented centralized logging using Spring AOP, capturing method execution details across services without polluting business logic.}
        \resumeItem{Database Design \& Optimization}
          {Worked with relational databases (e.g., PostgreSQL/MySQL), writing complex queries and optimizing schema for performance and scalability.}
        \resumeItem{Insurance Domain Logic}
          {Translated business requirements into backend logic involving premium calculations, policy underwriting rules, and claims validation.}
        \resumeItem{BDD \& Unit Testing}
          {Wrote tests using Cucumber and JUnit to validate business logic and maintain high code coverage; worked with QA to define test scenarios.}
        \resumeItem{Code Review \& Collaboration}
          {Reviewed code with a focus on verifying business logic correctness and functional alignment with requirements, contributing to overall code quality and maintainability.}        
        \resumeItem{Cloud}
          {Integrated backend services with cloud platforms such as Azure AI Search, EventHub, CosmosDB,... to enhance scalability and intelligence in enterprise apps.}
        \resumeItem{DevOps \& CI/CD Pipelines}
          {Participated in configuring deployment pipelines for backend services using GitHub Actions.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 -- Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd

%-------------------------------------------

    \resumeSubheading
      {VNG Corp}{Ho Chi Minh City}
      {Software Engineer}{May 2022 -- March 2023}
      \resumeItemListStart
        \resumeItem{TypeScript Migration}
          {Migrate the React Native project from JavaScript to TypeScript, improve code maintainability and type safety.}
        \resumeItem{Component Reusability}
          {Reduced code duplication and increased maintainability by building reusable and modular UI components.}
        \resumeItem{Performance Optimization}
          {Improved rendering performance using image caching, thumbnail previews, and data caching techniques to reduce load times and memory usage.}
        \resumeItem{React Reanimated Integration}
          {Implemented smooth and performant animations using React Reanimated for a better user experience.}
        \resumeItem{Firebase Push Notifications}
          {Integrated Firebase Cloud Messaging (FCM) to support real-time push notifications.}
        \resumeItem{State Management}
          {Managed complex application state using Redux Toolkit and MobX for scalable and reactive state handling.}
        \resumeItem{REST API Integration}
          {Developed features through RESTful API integration and collaborated with designers for accurate UI implementation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Attorney History}
      {Developed a system to search and retrieve attorney or law firm information using Azure AI Search for enhanced querying and indexing capabilities.}
    \resumeSubItem{Authorization Server}
      {Built an OAuth2-compliant Authorization Server using Spring Boot.}
    \resumeSubItem{File Tracking System}
      {Designed and implemented a microservice to monitor and log the movement of files across systems, ensuring traceability and auditability.}
    \resumeSubItem{MyVNG Application}
      {Created an internal web and mobile tool for VNG employees, serving functions similar to an HR portal, including personal information management and company services access.}
    \resumeSubItem{Mentorus Application}
      {Capstone graduation project - Developed a real-time chat application similar to Zalo, featuring messaging, user authentication, and contact management.}
  \resumeSubHeadingListEnd

%
%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Java, JavaScript, TypeScript, SQL}
    \resumeSubItem{Backend}
      {Spring Boot, JPA, REST APIs, OAuth2, AOP, JUnit, Mockito}
    \resumeSubItem{Frontend}
      {React, React Native, Redux Toolkit, MobX}
    \resumeSubItem{Cloud \& DevOps}
      {Azure (AI Search, EventHub, CosmosDB), GitHub Actions}
    \resumeSubItem{Databases}
      {MySQL, CosmosDB}
    \resumeSubItem{Testing}
      {BDD (Cucumber), Unit Testing, Code Coverage, Manual Code Review}
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}